
\documentclass{article}
\usepackage{amsmath}
\usepackage[margin=1in]{geometry}
\begin{document}
\begin{center}
    \textbf{IA5 - Introdution to Machine Learning}\\
\end{center}

\begin{flushleft}
\textbf{Date:} 2025-02-12 \quad \textbf{Faculty:} Mithun AV \hfill \textbf{Max Marks:} 16 \quad \textbf{Duration:} 60 mins
\end{flushleft}


\section{Part A}
Answer all the questions in this section.Each question carries one mark

\textbf{Q1:} What is d? \hfill Marks: 1 \\
\hspace*{\fill}[CO1]

\textbf{Q2:} What is c? \hfill Marks: 1 \\
\hspace*{\fill}[CO1]

\textbf{Q3:} What is b? \hfill Marks: 1 \\
\hspace*{\fill}[CO1]


\section{Part B}
Answer any two questions from this section.Each question carries 2 marks

\textbf{Q1:} Define the hypothesis function in linear regression. Write its mathematical representation. \hfill Marks: 2 \\
\hspace*{\fill}[CO2]

\textbf{Q2:} What is the cost function in linear regression and why is it used? \hfill Marks: 2 \\
\hspace*{\fill}[CO2]

\textbf{Q3:} State Bayes’ Theorem and its importance in Machine Learning. \hfill Marks: 2 \\
\hspace*{\fill}[CO3]


\section{Part C}
Answer any two question from this section.Each question carries 3 marks

\textbf{Q1:} Derive the update rule for gradient descent in linear regression. \hfill Marks: 3 \\
\hspace*{\fill}[CO2]

\textbf{Q2:} Explain the difference between L1 and L2 regularization techniques. \hfill Marks: 3 \\
\hspace*{\fill}[CO3]

\textbf{Q3:} What is the softmax function? Write its formula and explain its usage. \hfill Marks: 3 \\
\hspace*{\fill}[CO6]


\section{Part D}
Answer only one question from the following section.Each question carries 5 marks

\textbf{Q1:} Explain the working of Support Vector Machines (SVM) and the concept of the margin. \hfill Marks: 5 \\
\hspace*{\fill}[CO4]

\textbf{Q2:} Explain the concept of a neural network with an example of backpropagation. \hfill Marks: 5 \\
\hspace*{\fill}[CO3]


\end{document}
